---
title: "Analysis exercise: summary notes"
output: 
  html_document:
    toc: true
    toc_float: 
      collapsed: false
    toc_depth: 5
---

**IMPORTANT:** The following summaries require the model objects exported from `brms` to exist. Therefore to run the summaries, you need to first run the script `analysis_models.Rmd` that creates these objects. 

**IMPORTANT:** The original dataset collected information about university name which was then paired with a world rank. Both of these variables could be used to identify participants at institutions which, at the time, did not tie on ranks with any other institutions. Because of this, the variables were removed from the dataset. 

The variable `world_rank` was replaced with a randomly generated variable that correlated with the original rank with r = 0.9. Therefore the code below will still be able to run, however please note that any computations that use `world_rank` will not be exactly reproducible. 

The main analysis in the file `analysis_models.Rmd` uses the actual data that was used to fit the models reported in the manuscript. The statistical models used a categorical version of the variable (`world_rank` split into 4 levels), which doesn't pose risk of de-identification and was therefore retained. Basically, the statistical models `analysis_models.Rmd` can be reproduced exactly, but not the imputation. 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, fig.align = "center")

library(dplyr)
library(ggplot2)
library(magrittr)
library(mice)
library(brms)

library(tidybayes)
library(HDInterval)

source("../scripts/helpers.R")

data <- readRDS("../data/processed_data/analysis_exercise_processed_data_2021_10_07_world_rank_de-identified.rds")
imp_data_0 <- readRDS("../data/processed_data/imp_data_0_world_rank_removed.rds")

mod_out_mi <- readRDS("../objects/models/mod_out_mi_220322.rds")
mod_norm_mi <- readRDS("../objects/models/mod_norm_mi_220322.rds")
mod_het_mi <- readRDS("../objects/models/mod_het_mi_220322.rds")
mod_inf_mi_s1 <- readRDS("../objects/models/mod_inf_mi_s1_220322.rds")
mod_inf_mi_s2 <- readRDS("../objects/models/mod_inf_mi_s2_220322.rds")


env <- new.env()
```

Process original data for descriptives and plotting 

```{r}
data %<>%
  dplyr::mutate(
    
    demo_level = case_when(
      ri_teach == "Yes" & demo_level == "Faculty" ~ "Faculty who teach methods",
      TRUE ~ demo_level
    ),
    
    plot = if_else(plot == "No plot of raw data", 0, 1), 
    
    across(.cols = c(scenario, demo_level, ri_subfield), 
           .fns = factor), 
    # across(.cols = c(cat_norm, cat_het, cat_out, cat_inf),
    #       .fns = ordered_factor),
    
    scenario = factor(scenario, labels = c("Experimental", "Cross-sectional")), 
    ri_subfield = forcats::fct_relevel(ri_subfield, "Methods and meta-science", after = 0L), 
    demo_level = factor(demo_level, levels = c("Faculty who teach methods", "Faculty", 
                                               "Postdoctoral researcher", "PhD researcher", 
                                               "Postgraduate taught student", "Nonacademic researcher")), 

    # world_rank = case_when(
    #   rank == -99 ~ as.integer(1500), 
    #   rank == -999 ~ as.integer(-999), 
    #   is.na(rank) ~ as.integer(NA),
    #   TRUE ~ world_rank
    # ), 
    # uni_rank_cat = case_when(
    #   world_rank == 1500 ~ 4, 
    #   world_rank %in% c(501:1001) ~ 3,
    #   world_rank %in% c(201:500) ~ 2,
    #   world_rank %in% c(1:200) ~ 1
    # )
  ) #%>% 
 # dplyr::select(-rank)

model_data <- data %>% 
  dplyr::filter(ri_subfield != "Forensic psychology" | is.na(ri_subfield), 
                demo_level != "Postgraduate taught student" | is.na(demo_level), 
                world_rank != -999 | is.na(world_rank)) %>% 
  dplyr::mutate(
    demo_level = droplevels(demo_level), 
    ri_subfield = droplevels(ri_subfield)
  )
```


```{r}
env$data <- data
env$model_data <- model_data
env$imp_data_0 <- imp_data_0
```


```{r}
model_data %>% 
  dplyr::group_by(demo_level) %>% 
  dplyr::summarise(n = n()/2)
```


## Descriptives 

```{r}
re_plot_data <- imp_data_0 %>% 
  dplyr::select(id, scenario, cat_out, cat_inf, cat_norm, cat_het) %>%
  tidyr::pivot_longer(
    cols = c(cat_out, cat_inf, cat_norm, cat_het), 
    names_to = "assumption", 
    values_to = "practice_cat"
  ) %>%
  #dplyr::filter(!is.na(practice_cat)) %>% 
  dplyr::group_by(assumption, id) %>%
  dplyr::arrange(assumption, id, scenario) %>%
  dplyr::mutate(
    practice_diff = (as.numeric(practice_cat)[2] - as.numeric(practice_cat)[1]) %>% factor(., levels = c(-2, -1, 0, 1, 2)),
    assumption = factor(assumption, levels = c("cat_out", "cat_inf", "cat_norm", "cat_het"))
  ) %>% 
  dplyr::arrange(assumption, id, scenario) # repeating this so position_jitter of geoms aligns 
re_plot_data
```

#### Counts per group 

```{r}
re_plot_data %>% 
  dplyr::group_by(assumption, scenario, practice_cat) %>% 
  dplyr::summarise(n = n()) %>% 
  tidyr::pivot_wider(
    id_cols = c("practice_cat", "scenario"), 
    values_from = "n",
    names_from = "assumption"
  ) %>% 
  dplyr::arrange(practice_cat, scenario) %>% 
  lazy_kable()
```

#### Counts per change 

```{r}
re_plot_data %>%
  dplyr::filter(scenario == "s1") %>%
  dplyr::group_by(assumption, practice_diff) %>%
  dplyr::summarise(n = n()) %>% 
  tidyr::pivot_wider(
    id_cols = c("practice_diff"), 
    values_from = "n",
    names_from = "assumption"
  ) %>% 
  dplyr::arrange(practice_diff) %>% 
  lazy_kable()
```

```{r fig.height = 8, fig.width = 12}
re_plot_data %>% 
  dplyr::filter(!is.na(practice_cat)) %>% 
  
  ggplot2::ggplot(data = ., aes(x = scenario, y = practice_cat, group = id, colour = practice_diff)) + 
  geom_line(position = position_jitter(width = 0.15, height = 0.2, seed = 208), alpha = 0.3) + 
  geom_point(position = position_jitter(width = 0.15, height = 0.2, seed = 208), alpha = 0.2) + 
  scale_colour_manual(values = c("#b8002b", "#610017", "#cccccc", "#cfad72", "#c9902c", "black")) + 
  facet_wrap(~assumption) + 
  theme_minimal() + 
  theme(
    text = element_text(size = 16)
  )
```

## Models 

### Raw summaries 

#### Outliers

```{r}
mod_out_mi_summary <- summary(mod_out_mi)

mod_out_effects_scenario <- conditional_effects(mod_out_mi, "scenario", categorical = T)
mod_out_effects_level <- conditional_effects(mod_out_mi, "demo_level", categorical = T)
mod_out_effects_uni <- conditional_effects(mod_out_mi, "uni_rank_cat", categorical = T)

mod_out_mi_summary$fixed[ ,1:4] %>% lazy_kable()

mod_out_effects_scenario
mod_out_effects_level
mod_out_effects_uni
```

#### Influential cases 

##### With random effects (1|id)

```{r}
mod_inf_mi_re_summary <- summary(mod_inf_mi_re)

mod_inf_re_effects_scenario <- conditional_effects(mod_inf_mi_re, "scenario", categorical = T)
mod_inf_re_effects_level <- conditional_effects(mod_inf_mi_re, "demo_level", categorical = T)
mod_inf_re_effects_uni <- conditional_effects(mod_inf_mi_re, "uni_rank_cat", categorical = T)

mod_inf_mi_re_summary$fixed[ ,1:4] %>% lazy_kable()

mod_inf_re_effects_scenario
mod_inf_re_effects_level
mod_inf_re_effects_uni
```

##### No random effects (keep s1 and s2)

```{r}
mod_inf_mi_summary <- summary(mod_inf_mi)

mod_inf_effects_scenario <- conditional_effects(mod_inf_mi, "scenario", categorical = T)
mod_inf_effects_level <- conditional_effects(mod_inf_mi, "demo_level", categorical = T)
mod_inf_effects_uni <- conditional_effects(mod_inf_mi, "uni_rank_cat", categorical = T)

mod_inf_mi_summary$fixed[ ,1:4] %>% lazy_kable()

mod_inf_effects_scenario
mod_inf_effects_level
mod_inf_effects_uni
```

##### s1 only 

```{r}
mod_inf_mi_s1_summary <- summary(mod_inf_mi_s1)
mod_inf_mi_s2_summary <- summary(mod_inf_mi_s2)

mod_inf_s1_effects_level <- conditional_effects(mod_inf_mi_s1, "demo_level", categorical = T)
mod_inf_s1_effects_uni <- conditional_effects(mod_inf_mi_s1, "uni_rank_cat", categorical = T)

mod_inf_mi_s1_summary$fixed[ ,1:4] %>% lazy_kable()

mod_inf_s1_effects_level
mod_inf_s1_effects_uni
```

#### Normality

```{r}
mod_norm_mi_summary <- summary(mod_norm_mi)
```

#### Heterogeneity 

```{r}
mod_het_mi_summary <- summary(mod_het_mi)
```

```{r}
env$mod_norm_mi_summary <- mod_norm_mi_summary
env$mod_het_mi_summary <- mod_het_mi_summary
env$mod_out_mi_summary <- mod_out_mi_summary
env$mod_inf_mi_s1_summary <- mod_inf_mi_s1_summary
env$mod_inf_mi_s2_summary <- mod_inf_mi_s2_summary
```


## Overall plots (descriptive)

```{r}
base_plots_data <- model_data %>% 
  dplyr::select(
    id, scenario, cat_norm, cat_het, cat_out, cat_inf
  ) %>%
  tidyr::pivot_longer(
    ., 
    cols = c(cat_norm:cat_inf), 
    names_to = "assumption", 
    values_to = "practice_cat"
  ) %>%
  dplyr::mutate(
    assumption = factor(assumption, 
                          levels = c("cat_norm", "cat_het", "cat_out", "cat_inf"), 
                          labels = c("Normality", "Homoscedasticity", "Basic checks and outliers", "Influential cases"))
  )

base_plots_sum <- base_plots_data %>% 
  dplyr::group_by(scenario, assumption, practice_cat) %>%
  dplyr::summarise(
    n = n()
  ) %>%
  dplyr::group_by(scenario, assumption) %>%
  dplyr::mutate(
    prop = n/sum(n), 
    percent = prop * 100)
```

### Plot set up 

```{r}
col_main = "#1c4c72"
col_main_contrast = "#e7a350"
col_background = "#fee8d1"
col_gridlines = "#e3d0bc"
col_text = "#5e5e5e"
axis_text_size = 12
axis_title_size = 12
strip_text_size= 12

col_point_range = col_main
col_t3 = "#E7C496"
col_t2 = col_main_contrast
col_t1 = "#c57c43"

theme_set_up = theme(
  axis.title.y = element_text(margin = margin(t = 0, r = 5, b = 0, l = 0)),
  axis.title.x = element_text(margin = margin(t = 10, r = 0, b = 0, l = 0)),
  
  panel.background = element_rect(colour = col_background, fill = col_background), 
  plot.background = element_rect(colour = col_background, fill = col_background), 
  panel.grid.major = element_line(colour = col_gridlines), 
  panel.grid.minor = element_blank(),
  
  strip.background = element_rect(fill = col_main), 
  strip.text = element_text(face = "bold", size = strip_text_size), 
  
  legend.background = element_rect(fill = col_background),
  legend.text = element_text(colour = col_text),
  legend.title = element_text(face = "bold", colour = col_text),
  axis.title = element_text(face = "bold", colour = col_text, size = axis_title_size),
  axis.text = element_text(colour = col_text, size = axis_text_size),
  
  legend.position = "none"
  
) 
```


```{r fig.width=6, fig.height=6, warning = FALSE}
#base_plot_wide <- 
#base_plot_long <- 
base_plot_square <- 
  base_plots_sum %>%
  ggplot2::ggplot(., aes(x = practice_cat, y = percent, colour = scenario, fill = scenario)) +
  geom_col(position = position_dodge(width = 0.7), width = 0.5) + 
  facet_wrap(~assumption, nrow = 2) +
  scale_fill_manual(values = rev(c(col_main, col_main_contrast))) + 
  scale_colour_manual(values = rev(c(col_main, col_main_contrast))) + 
  
  labs(x = "Practice category (1-5)", y = "Percent (%)", colour = "Scenario", fill = "Scenario") + 
  
  coord_cartesian(ylim = c(0, 100)) + 
  scale_y_continuous(breaks = seq(0, 100, 25)) + 
  
  theme_light() + 
  theme_set_up 

base_plot_square

# ggplot2::ggsave(base_plot_wide, filename =  "../figures/base_plot_wide.png",
#                 width = 12, height = 3.5)
# 
# ggplot2::ggsave(base_plot_long, filename =  "../figures/base_plot_long.png",
#                 width = 3.5, height = 12)
# 
# ggplot2::ggsave(base_plot_square, filename =  "../figures/base_plot_square.png",
#                 width = 6, height = 6)
  

```















### Probit model summaries

#### Research level 

(Subtract each effect from the intercepts, then $exp(x) / (1 + exp(x))$ to get cumulative probabilities)


```{r}
get_plot_data_old <- function(model_sum, effect_string, levels, assumption){
  
  mod_df <- model_sum$fixed[ , c(1,3,4)] %>% 
  as.data.frame()
  
  #####
  
  intercepts <- mod_df[1:2, ]
  nrow = nrow(mod_df)
  
  effects_rev <- mod_df[3:nrow, ] * (-1)
  effects_t1 <- effects_rev + intercepts[rep(1, times = nrow-2), ]
  effects_t2 <- effects_rev + intercepts[rep(2, times = nrow-2), ]
  
  effects_all <- dplyr::bind_rows(
    intercepts %>% dplyr::mutate(threshold = c("t1", "t2")) %>% tibble::rownames_to_column(), 
    effects_t1 %>% dplyr::mutate(threshold = "t1") %>% tibble::rownames_to_column(), 
    effects_t2 %>% dplyr::mutate(threshold = "t2") %>% tibble::rownames_to_column()
  ) 
  
  
  if(nrow(effects_all) == 16){order = c(1,2,rep(c(3,4,5,6,7,8,9), 2))}
  else{order = c(1,2,rep(c(3,4,5,6,7, 8), 2))}
  
  effects_all %<>%
  dplyr::mutate(order = order)
  
  effects_all %<>%
    dplyr::mutate(
      Estimate = brms::inv_logit_scaled(Estimate), 
      `l-95% CI` = brms::inv_logit_scaled(`l-95% CI`, ub = Estimate), 
      `u-95% CI` = brms::inv_logit_scaled(`u-95% CI`, lb = Estimate), 
    ) %>% 
    dplyr::arrange(order)
  
  # important note on the calculation of the CIs above - at the moment, I'm just using the same inverse logit 
  # function for all CIs with lower and upper bounds. The CIs for the intercepts however compute correctly
  # without lower and upper bounds. As in, they match the output from brms::conditional_effects. Basically, 
  # I need to find the correct way to subtract the estimates from the intercepts in a way that doesn't cause
  # the point estimate to be outside of the confidence intervals after conversion by inv_logit
  
  #####
  
  predictor_effects <- effects_all %>% 
  dplyr::filter(stringr::str_detect(rowname, paste0("Intercept|", effect_string))) %>% 
    dplyr::arrange(order) 
  
  nrow_effects <- nrow(predictor_effects)
  
  levels = levels
  
  predictor_effects[(nrow_effects+1):(nrow_effects+length(levels)), ] <- NA
  
  predictor_effects %<>% 
    dplyr::mutate(
      rowname = c(rep(levels, each = 2), levels),
      threshold = c(threshold[1:nrow_effects], rep("t3", length(levels))), 
      Estimate = c(Estimate[1:nrow_effects], rep(1, length(levels))) * 100,
      `l-95% CI` = `l-95% CI` * 100,
      `u-95% CI` = `u-95% CI` * 100
    ) %>% 
     dplyr::arrange(rowname) %>% 
    dplyr::group_by(rowname) %>%
    dplyr::mutate(
      plot_estimate = Estimate - lag(Estimate),
      plot_estimate = if_else(is.na(plot_estimate), Estimate, plot_estimate), 
      rowname = factor(rowname, levels = levels),
      assumption = assumption
    )
  
}
```


```{r}
plot_data_level_1 <- get_plot_data(model = mod_norm_mi, effect_string = "demo_level", 
                                   levels = c("Teach", "Faculty", "Postdoc", "PhD"), 
                                   assumption = "Normality")

plot_data_level_2 <- get_plot_data(model = mod_het_mi, effect_string = "demo_level", 
                                   levels = c("Teach", "Faculty", "Postdoc", "PhD"), 
                                   assumption = "Homoscedasticity")

plot_data_level_3 <- get_plot_data(model = mod_out_mi, effect_string = "demo_level", 
                                   levels = c("Teach", "Faculty", "Postdoc", "PhD"), 
                                   assumption = "Basic checks and outliers")

plot_data_level_4 <- get_plot_data(model = mod_inf_mi_s1, effect_string = "demo_level", 
                                   levels = c("Teach", "Faculty", "Postdoc", "PhD"), 
                                   assumption = "Influential cases (experimental)")

plot_data_level_5 <- get_plot_data(model = mod_inf_mi_s2, effect_string = "demo_level", 
                                   levels = c("Teach", "Faculty", "Postdoc", "PhD"), 
                                   assumption = "Influential cases (cross-sectional)")

plot_data_level_merged <- 
  dplyr::bind_rows(
    plot_data_level_1, 
    plot_data_level_2, 
    plot_data_level_3, 
    plot_data_level_4, 
    plot_data_level_5
  ) %>%
  dplyr::mutate(
    assumption = factor(assumption, 
                        levels = c("Normality", "Homoscedasticity", "Basic checks and outliers", "Influential cases (experimental)", "Influential cases (cross-sectional)")), 
    rowname = factor(rowname, 
                     levels = c("Teach", "Faculty", "Postdoc", "PhD"),
                     labels = c("Methods \ninstructors", "Faculty", "Postdocs", "PhDs")), 
    threshold = factor(threshold, 
                       levels = c("t3", "t2", "t1"),
                       labels = c("\nCorrect checks are performed \n \n", 
                                  "Some checks are performed \nbut they are insufficient \nto detect problems\n", 
                                  "No action taken / \nno checks are performed")
                      )
  )

plot_data_level_merged
```




```{r fig.width=12, fig.height=3.5}
col_point_range = col_main
col_t3 = "#E7C496"
col_t2 = col_main_contrast
col_t1 = "#c57c43"

dodge_width = -0.8
error_bar_width = 0.2

#e7a350

plot_data = plot_data_level_merged

level_plot_wide <- 
#level_plot_long <- 
#level_plot_square <- 
  ggplot2::ggplot(data = plot_data, aes(x = rowname, 
                                      fill = threshold, 
                                      y = plot_estimate)) + 
  geom_bar(stat = "identity",
           width = 0.3, size = 0.01) + 
  
  geom_point(data = plot_data %>% 
               dplyr::filter(threshold != levels(plot_data$threshold)[1]), 
             aes(x = rowname, y = Estimate), 
             colour = col_point_range, 
             position = position_dodge(width = dodge_width), 
             show.legend = FALSE, 
             
  ) + 
    geom_errorbar(data = plot_data %>% 
                    dplyr::filter(threshold != levels(plot_data$threshold)[1]),
                  aes(x = rowname, ymin = `l-95% CI`, ymax = `u-95% CI`),
                  colour = col_point_range,
                  width = error_bar_width,
                  position = position_dodge(width = dodge_width)
                  ) +
    
    scale_fill_manual(values = c(col_t3, col_t2, col_t1)) + 
    
    labs(x = "Academic research level", y = "Cumulative percent (%)", fill = "Practice quality") + 
    facet_wrap(~assumption, ncol = 4) + 
    theme_light() +
    theme_set_up + 
    theme(
      legend.spacing.y = unit(.5, "cm"), 
      legend.key = element_rect(size = 10, colour = col_background, fill = col_background),
      legend.key.size = unit(1, "cm"),
      axis.text.x = element_text(angle = 0, colour = col_text, size = 11.5), 
      panel.grid.minor = element_line(colour = col_gridlines)
    )

level_plot_wide

# 
# ggplot2::ggsave(level_plot_wide, filename =  "../figures/level_plot_wide.png",
#                 width = 12, height = 3.5)
#  
# ggplot2::ggsave(level_plot_long, filename =  "../figures/level_plot_long.png",
#                 width = 3.5, height = 12)
# 
# ggplot2::ggsave(level_plot_square, filename =  "../figures/level_plot_square.png",
#                 width = 6, height = 6)
  

```


#### scenario

```{r}
plot_data_scenario_1 <- get_plot_data(model = mod_norm_mi, effect_string = "scenario", 
                                   levels = c("s1", "s2"), 
                                   assumption = "Normality")

plot_data_scenario_2 <- get_plot_data(model = mod_het_mi, effect_string = "scenario", 
                                   levels = c("s1", "s2"), 
                                   assumption = "Homoscedasticity")

plot_data_scenario_3 <- get_plot_data(model = mod_out_mi, effect_string = "scenario", 
                                   levels = c("s1", "s2"), 
                                   assumption = "Basic checks and outliers")

plot_data_scenario_4 <- get_plot_data(model = mod_inf_mi_s1, effect_string = "scenario", 
                                   levels = c("s1"), 
                                   assumption = "Influential cases (experimental)")

plot_data_scenario_5 <- get_plot_data(model = mod_inf_mi_s2, effect_string = "scenario", 
                                   levels = c("s2"), 
                                   assumption = "Influential cases (cross-sectional)")

plot_data_scenario_merged <- 
  dplyr::bind_rows(
    plot_data_scenario_1, 
    plot_data_scenario_2, 
    plot_data_scenario_3, 
    plot_data_scenario_4,
    plot_data_scenario_5
  ) %>%
  dplyr::mutate(
    assumption = factor(assumption, 
                        levels = c("Normality", "Homoscedasticity", "Basic checks and outliers", "Influential cases (experimental)", "Influential cases (cross-sectional)")), 
    rowname = factor(rowname, 
                     levels = c("s1", "s2"),
                     labels = c(" Experimental \nscenario", " Cross-sectional \nscenario")), 
    threshold = factor(threshold, 
                       levels = c("t3", "t2", "t1"),
                       labels = c("\nCorrect checks are performed \n \n", 
                                  "Some checks are performed \nbut they are insufficient \nto detect problems\n", 
                                  "No action taken / \nno checks are performed")
                      )
  )
```


#### University rank

```{r}
plot_data_rank_1 <- get_plot_data(model = mod_norm_mi, effect_string = "uni_rank", 
                                   levels = c("1", "2", "3", "4"), 
                                   assumption = "Normality")

plot_data_rank_2 <- get_plot_data(model = mod_het_mi, effect_string = "uni_rank", 
                                   levels = c("1", "2", "3", "4"), 
                                   assumption = "Homoscedasticity")

plot_data_rank_3 <- get_plot_data(model = mod_out_mi, effect_string = "uni_rank", 
                                   levels = c("1", "2", "3", "4"), 
                                   assumption = "Basic checks and outliers")

plot_data_rank_4 <- get_plot_data(model = mod_inf_mi_s1, effect_string = "uni_rank", 
                                   levels = c("1", "2", "3", "4"), 
                                   assumption = "Influential cases (experimental)")
plot_data_rank_5 <- get_plot_data(model = mod_inf_mi_s2, effect_string = "uni_rank", 
                                   levels = c("1", "2", "3", "4"), 
                                   assumption = "Influential cases (cross-sectional)")

plot_data_rank_merged <- 
  dplyr::bind_rows(
    plot_data_rank_1, 
    plot_data_rank_2, 
    plot_data_rank_3, 
    plot_data_rank_4, 
    plot_data_rank_5
  ) %>%
  dplyr::mutate(
    assumption = factor(assumption, 
                        levels = c("Normality", "Homoscedasticity", "Basic checks and outliers", "Influential cases (experimental)", "Influential cases (cross-sectional)")), 
    rowname = factor(rowname, 
                     levels = c("1", "2", "3", "4"),
                     labels = c(" 1-\n200", " 201-\n500", "  501-\n1000", "Not \nranked")), 
    threshold = factor(threshold, 
                       levels = c("t3", "t2", "t1"),
                       labels = c("\nCorrect checks are performed \n \n", 
                                  "Some checks are performed \nbut they are insufficient \nto detect problems\n", 
                                  "No action taken / \nno checks are performed")
                      )
  )

plot_data_rank_merged
```

```{r}
env$plot_data_level_merged <- plot_data_level_merged
env$plot_data_scenario_merged <- plot_data_scenario_merged
env$plot_data_rank_merged <- plot_data_rank_merged
```



```{r fig.width=12, fig.height=3.5}

dodge_width = -0.8
error_bar_width = 0.2

#e7a350

plot_data = plot_data_rank_merged

rank_plot_wide <- 
#rank_plot_long <- 
#rank_plot_square <- 
  ggplot2::ggplot(data = plot_data, aes(x = rowname, 
                                      fill = threshold, 
                                      y = plot_estimate)) + 
  geom_bar(stat = "identity",
           width = 0.3, size = 0.01) + 
  
  geom_point(data = plot_data %>% 
               dplyr::filter(threshold != levels(plot_data$threshold)[1]), 
             aes(x = rowname, y = Estimate), 
             colour = col_point_range, 
             position = position_dodge(width = dodge_width), 
             show.legend = FALSE, 
             
  ) + 
  geom_errorbar(data = plot_data %>% 
               dplyr::filter(threshold != levels(plot_data$threshold)[1]),
               aes(x = rowname, ymin = `l-95% CI`, ymax = `u-95% CI`),
                colour = col_point_range,
                width = error_bar_width,
                position = position_dodge(width = dodge_width)) +
  
  scale_fill_manual(values = c(col_t3, col_t2, col_t1)) + 
  
  labs(x = "World rank (Times HE)", y = "Cumulative percent (%)", fill = "Practice quality") + 
  facet_wrap(~assumption, ncol = 4) + 
  theme_light() +
  theme_set_up + 
  theme(
     legend.spacing.y = unit(.5, "cm"), 
     legend.key = element_rect(size = 10, colour = col_background, fill = col_background),
     legend.key.size = unit(1, "cm"),
     axis.text.x = element_text(colour = col_text), 
    panel.grid.minor = element_line(colour = col_gridlines))


ggplot2::ggsave(rank_plot_wide, filename =  "../figures/rank_plot_wide.png",
                width = 12, height = 3.5)
#  
# ggplot2::ggsave(rank_plot_long, filename =  "../figures/rank_plot_long.png",
#                 width = 3.5, height = 12)
# 
# ggplot2::ggsave(rank_plot_square, filename =  "../figures/rank_plot_square.png",
#                 width = 6, height = 6)

```


```{r}
env$posterior_df_norm <- as.data.frame(mod_norm_mi) %>% HDInterval::hdi()
env$posterior_df_het <- as.data.frame(mod_het_mi) %>% HDInterval::hdi()
env$posterior_df_out <- as.data.frame(mod_out_mi) %>% HDInterval::hdi()
env$posterior_df_inf_s1 <- as.data.frame(mod_inf_mi_s1) %>% HDInterval::hdi()
env$posterior_df_inf_s2 <- as.data.frame(mod_inf_mi_s2) %>% HDInterval::hdi()
```


### Discrete probabilities 



```{r}
mod_norm_mi_conditional_probs <- conditional_probs(mod_norm_mi, "Normality")
mod_het_mi_conditional_probs <- conditional_probs(mod_het_mi, "Homoscedasticity")
mod_out_mi_conditional_probs <- conditional_probs(mod_out_mi, "Basic checks and outliers")
mod_inf_mi_conditional_probs <- conditional_probs_inf(mod_inf_mi_s1, mod_inf_mi_s2, "Influential cases")
```


```{r}
env$mod_norm_mi_conditional_probs <- mod_norm_mi_conditional_probs
env$mod_het_mi_conditional_probs <- mod_het_mi_conditional_probs
env$mod_out_mi_conditional_probs <- mod_out_mi_conditional_probs
env$mod_inf_mi_conditional_probs <- mod_inf_mi_conditional_probs
```


# Model plots 

scenario

```{r}
scenario_model_data <- 
  rbind.data.frame(
    mod_norm_mi_conditional_probs[[1]], 
    mod_het_mi_conditional_probs[[1]], 
    mod_out_mi_conditional_probs[[1]], 
    mod_inf_mi_conditional_probs[[1]]
    
  )

scenario_model_data %>% 
  ggplot2::ggplot(., aes(y = estimate, x = .category, colour = scenario)) + 
  geom_point(position = position_dodge(width = 0.4)) + 
  geom_errorbar(
    aes(ymin = lower_hpd, ymax = upper_hpd), 
    position = position_dodge(width = 0.4), 
    width = 0.2) + 
  facet_wrap(~assumption)
```

demo_level

```{r}
demo_level_model_data <- 
  rbind.data.frame(
    mod_norm_mi_conditional_probs[[2]], 
    mod_het_mi_conditional_probs[[2]], 
    mod_out_mi_conditional_probs[[2]], 
    mod_inf_mi_conditional_probs[[2]]
    
  )

demo_level_model_data %>% 
  ggplot2::ggplot(., aes(y = estimate, x = .category, colour = demo_level)) + 
  geom_point(position = position_dodge(width = 0.4)) + 
  geom_errorbar(
    aes(ymin = lower_hpd, ymax = upper_hpd), 
    position = position_dodge(width = 0.4), 
    width = 0.2) + 
  facet_wrap(~assumption)

```














```{r}
#env <- readRDS("../objects/env.rds")
```



```{r}
saveRDS(env, "../objects/env_220322.rds")
```



## HPD intervals 

Extract posterior draws

```{r}
mod_inf_post_df <-  as.data.frame(mod_inf_mi_s1)

mod_inf_post_df

summary(mod_inf_mi_s1)
```

```{r}
ggplot2::ggplot(mod_inf_post_df) + 
  geom_density(aes(x = (`b_Intercept[1]`) %>% exp_c()), colour = "blue") + 
  geom_density(aes(x = ((`b_demo_levelFaculty`*(-1)) + `b_Intercept[1]`) %>% exp_c()), colour = "green")
```

```{r}
HDInterval::hdi(mod_inf_post_df$`b_Intercept[1]`, .95)
```

```{r}
mod_inf_post_df %<>%
  dplyr::mutate(
    prob_c_intercept_1 = brms::inv_logit_scaled(`b_Intercept[1]`)
  )

```

Ammend `get_plot_data` 

```{r}
get_plot_data <- function(model, effect_string, levels, assumption){
#
# model = mod_out_mi
# effect_string = "demo_level"
# levels = c("Teach", "Faculty", "Postdoc", "PhD")
# assumption = "Influential cases"

  model_sum <- summary(model)
  
  mod_df <- model_sum$fixed[ , 1:2] %>% 
  as.data.frame()
  
  #####
  
  intercepts <- mod_df[1:2, ]
  nrow = nrow(mod_df)
  
  effects_rev <- mod_df[3:nrow, ] * (-1)
  effects_t1 <- effects_rev + intercepts[rep(1, times = nrow-2), ]
  effects_t2 <- effects_rev + intercepts[rep(2, times = nrow-2), ]
  
  effects_all <- dplyr::bind_rows(
    intercepts %>% dplyr::mutate(threshold = c("t1", "t2")) %>% tibble::rownames_to_column(), 
    effects_t1 %>% dplyr::mutate(threshold = "t1") %>% tibble::rownames_to_column(), 
    effects_t2 %>% dplyr::mutate(threshold = "t2") %>% tibble::rownames_to_column()
  ) 
  
  #### prepare for plots ####
  
  if(nrow(effects_all) == 16){order = c(1,2,rep(c(3,4,5,6,7,8,9), 2))}
  else{order = c(1,2,rep(c(3,4,5,6,7, 8), 2))}

  # order = c(1,2,rep(c(3,4,5,6,7,8,9), 2))
  # order = c(1,2,rep(c(3,4,5,6,7, 8), 2))
  
  effects_all %<>%
  dplyr::mutate(order = order)
  
  ##### get proper HPD intervals 

  model_post_df <- as.data.frame(model)
  
  # subtract each effect from intercepts 
  
  effect_names <- names(model_post_df)[stringr::str_detect(names(model_post_df), "scenario|demo_level|uni_rank")]
  
  # next - inverse and do plus intercept using across 
  
  rev_vals <- function(x){x*(-1)}
  
  hpd_t1 <- model_post_df %>% 
    dplyr::mutate(
      across(.cols = all_of(effect_names),
             .fns = rev_vals), 
      across(.cols = all_of(effect_names), 
             .fns = ~.x + `b_Intercept[1]`), 
      across(.cols = c("b_Intercept[1]", all_of(effect_names)), 
             .fns = exp_c)
    ) %>%
    dplyr::select(-c(`b_Intercept[2]`, disc, lp__)) %>%
    HDInterval::hdi(credMass = .95) %>% 
    t() %>%
    as.data.frame() %>%
    tibble::rownames_to_column() %>%
    dplyr::mutate(
      threshold = "t1", 
      rowname = stringr::str_remove_all(rowname, pattern = "b_")
    )
  
  hpd_t2 <- model_post_df %>% 
    dplyr::mutate(
      across(.cols = all_of(effect_names),
             .fns = rev_vals), 
      across(.cols = all_of(effect_names), 
             .fns = ~.x + `b_Intercept[2]`), 
      across(.cols = c("b_Intercept[2]", all_of(effect_names)), 
             .fns = exp_c)
    ) %>%
    dplyr::select(-c(`b_Intercept[1]`, disc, lp__)) %>%
    HDInterval::hdi(credMass = .95) %>% 
    t() %>%
    as.data.frame() %>%
    tibble::rownames_to_column() %>%
    dplyr::mutate(
      threshold = "t2", 
      rowname = stringr::str_remove_all(rowname, pattern = "b_")
    )
    
  hpd_df <- dplyr::full_join(hpd_t1, hpd_t2, by = c("rowname", "lower", "upper", "threshold")) %>%
    dplyr::filter(rowname %in% effects_all$rowname)
  
  effects_all %<>% dplyr::full_join(., hpd_df, c("rowname", "threshold"))
  
  effects_all %<>%
    dplyr::mutate(
      Estimate = brms::inv_logit_scaled(Estimate), 
      `l-95% CI` = lower, 
      `u-95% CI` = upper, 
    ) %>% 
    dplyr::arrange(order)
  
  effects_all
  
  #####
  
  predictor_effects <- effects_all %>% 
  dplyr::filter(stringr::str_detect(rowname, paste0("Intercept|", effect_string))) %>% 
    dplyr::arrange(order) 
  
  nrow_effects <- nrow(predictor_effects)
  
  levels = levels
  
  predictor_effects[(nrow_effects+1):(nrow_effects+length(levels)), ] <- NA
  
  predictor_effects %<>% 
    dplyr::mutate(
      rowname = c(rep(levels, each = 2), levels),
      threshold = c(threshold[1:nrow_effects], rep("t3", length(levels))), 
      Estimate = c(Estimate[1:nrow_effects], rep(1, length(levels))) * 100,
      `l-95% CI` = `l-95% CI` * 100,
      `u-95% CI` = `u-95% CI` * 100
    ) %>% 
     dplyr::arrange(rowname) %>% 
    dplyr::group_by(rowname) %>%
    dplyr::mutate(
      plot_estimate = Estimate - lag(Estimate),
      plot_estimate = if_else(is.na(plot_estimate), Estimate, plot_estimate), 
      rowname = factor(rowname, levels = levels),
      assumption = assumption
    )
  
  
  
}
```

