---
title: "data_analysis"
author: "MS"
date: "06/09/2021"
output: html_document
---

IMPORTANT: The original dataset collected information about university name which was then paired with a world rank. Both of these variables could be used to identify participants at institutions which, at the time, did not tie on ranks with any other institutions. Because of this, the variables were removed from the dataset. 

The variable `world_rank` was replaced with a randomly generated variable that correlated with the original rank with r = 0.9. Therefore the code below will still be able to run, however please note that any computations that use `world_rank` will not be exactly reproducible. 

The main analysis in the file `analysis_models.Rmd` uses the actual data that was used to fit the models reported in the manuscript. The statistical models used a categorical version of the variable (`world_rank` split into 4 levels), which doesn't pose risk of de-identification and was therefore retained. Basically, the statistical models `analysis_models.Rmd` can be reproduced exactly, but not the imputation. 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(brms)
library(dplyr)
library(ggplot2)
library(magrittr)
library(mice)

imp_data_long <- readRDS("../data/processed_data/imp_data_long_101021_world_rank_removed.rds")

exp_c <- function(x){round(1/(1 + exp(x)), 3)}
```

# Prepare data for analysis 

```{r}
ordered_factor <- function(x){
  x = factor(x, ordered = TRUE, levels = c(1,2,3))
  return(x)
  }

imp_data_long %<>%
  dplyr::mutate(
    id = factor(id),
    across(
      .cols = cat_norm:cat_inf,
      .fns = ordered_factor
    ), 
    # uni_rank_cat = case_when(
    #   world_rank == 1500 ~ 4, 
    #   world_rank %in% c(501:1001) ~ 3,
    #   world_rank %in% c(201:500) ~ 2,
    #   world_rank %in% c(1:200) ~ 1
    # ) %>% factor(), 
    row_names = rownames(.)
  ) %>%
  dplyr::group_by(.imp) %>%
  dplyr::mutate(.id = 1:max(row_number())) %>% 
  dplyr::ungroup() 


imp_data_0 <- imp_data_long %>%
  dplyr::filter(.imp == 0)

imp_data_1 <- imp_data_long %>%
  dplyr::filter(.imp == 1)

imp_data_im <- mice::as.mids(long = imp_data_long)
```

```{r}
#saveRDS(imp_data_0, "../data/processed_data/imp_data_0.rds")
```


# Random slopes plots 

```{r fig.height = 8}
re_plot_data <- imp_data_0 %>% 
  dplyr::select(id, scenario, cat_out, cat_inf, cat_norm, cat_het) %>%
  tidyr::pivot_longer(
    cols = c(cat_out, cat_inf, cat_norm, cat_het), 
    names_to = "assumption", 
    values_to = "practice_cat"
  ) %>%
  dplyr::filter(!is.na(practice_cat)) %>% 
  dplyr::group_by(assumption, id) %>%
  dplyr::arrange(assumption, id, scenario) %>%
  dplyr::mutate(
    practice_diff = (as.numeric(practice_cat)[2] - as.numeric(practice_cat)[1]) %>% factor(., levels = c(-2, -1, 0, 1, 2))
  )
  
ggplot2::ggplot(data = re_plot_data , aes(x = scenario, y = practice_cat, group = id, colour = practice_diff)) + 
  geom_line(position = position_jitter(width = 0.15, height = 0.2, seed = 208), alpha = 0.3) + 
  geom_point(position = position_jitter(width = 0.15, height = 0.2, seed = 208), alpha = 0.2) + 
  scale_colour_manual(values = c("#b8002b", "#610017", "#cccccc", "#cfad72", "#c9902c", "black")) + 
  facet_wrap(~assumption) + 
  theme_light()



```

```{r}
re_plot_data %>%
  dplyr::filter(scenario == "s1") %>%
  dplyr::group_by(assumption, practice_diff) %>%
  dplyr::summarise(n = n()) %>%
  dplyr::group_by(assumption) %>% 
  dplyr::group_split()
```


# Fit models

```{r}
imp_data_list <- imp_data_long %>% 
  dplyr::filter(., .imp != 0) %>%
  dplyr::group_by(.imp) %>%
  dplyr::group_split()


imp_data_list <- purrr::map(.x = imp_data_list, .f = as.data.frame)

```

## outliers

```{r}
mod_out_1 <- brms::brm(
  formula = 
    cat_out ~ 1 + demo_level + scenario + uni_rank_cat + (1|id),
  data = imp_data_list[[1]], 
  family = cumulative("probit"), 
  cores = 4
)
```

```{r}
exp_c <- function(x){round(1/(1 + exp(x)), 3)}

re_draws_1_out <- coda::as.mcmc(mod_out_1)[[1]] %>%
  as.data.frame() %>%
  dplyr::select(contains("id")) %>%
  dplyr::mutate(
    across(.fns = exp_c)
  ) %>%
  tidyr::pivot_longer(
    cols = everything(),
    values_to = "prob", 
    names_to = "re"
  )

for(i in unique(as.character(data_1$id))){
  
  print(  
    re_draws_1_out %>%
      dplyr::filter(stringr::str_detect(string = re, pattern = i)) %>%
      ggplot2::ggplot(data = ., aes(x = prob)) + 
      labs(title = i) + 
      geom_density(size = 2) + 
      theme(
        plot.title = element_text(size = 60)
      )
  )
  
}

```

```{r}
imp_data_list[[1]] %>%
  dplyr::group_by(scenario, cat_out) %>%
  dplyr::summarise(n = n()) %>%
  dplyr::group_by(scenario)%>%
  dplyr::mutate(
    percent = n/ sum(n)
  )

summary(mod_out_1)
conditional_effects(mod_out_1, categorical = TRUE, ask = FALSE)
```

```{r}
mod_out_fixed <- brms::brm(
  formula = 
    cat_out ~ 1 + demo_level + scenario + uni_rank_cat,
  data = imp_data_list[[1]], 
  family = cumulative("probit"), 
  cores = 4
)
```

```{r}
summary(mod_out_fixed)
conditional_effects(mod_out_fixed, categorical = TRUE, ask = FALSE)
```


```{r}
set.seed(30)
mod_out_mi <- brms::brm_multiple(
  formula = 
    cat_out ~ 1 + demo_level + scenario + uni_rank_cat + (1|id),
  data = imp_data_list, 
  family = cumulative("probit"), 
  cores = 4
)



#saveRDS(mod_out_mi, "../objects/models/mod_out_mi_220322.rds")


```

```{r}
summary(mod_out_mi)
```

```{r}
round(mod_out_mi$rhats, 2)
```

## influential cases 

```{r}
imp_data_0 %>% 
  dplyr::select(id, scenario, demo_level, uni_rank_cat, cat_inf) %>%
  dplyr::group_by(cat_inf) %>%
  dplyr::summarise(
    n = n()
  )

```


```{r}
set.seed(30)

mod_inf_1 <- brms::brm(
  formula = 
    cat_inf ~ 1 + demo_level + scenario + uni_rank_cat+ (1|id)
  ,
  data = imp_data_list[[1]],
  family = cumulative("probit"), 
  cores = 4
)

#saveRDS(mod_inf_1, "../objects/models/mod_inf_1_re_bad.rds")
```

```{r}
summary(mod_inf_1)
```

```{r}
conditional_effects(mod_inf_1, categorical = TRUE)
```


```{r}
mod_inf_mi <- brms::brm_multiple(
  formula = 
    cat_inf ~ 1 + demo_level + scenario + uni_rank_cat,
  data = imp_data_im, 
  family = cumulative("probit"), 
  cores = 4
)


#saveRDS(mod_inf_mi, "../objects/models/mod_inf_mi_101121.rds")
```

```{r}
summary(mod_inf_mi)
```

```{r}
round(mod_inf_mi$rhats, 2)
```

s1 only: 

```{r}
imp_data_im_s1 <- mice::as.mids(long = imp_data_long %>% dplyr::filter(scenario == "s1"))
```

```{r}
mod_inf_mi_s1 <- brms::brm_multiple(
  formula = 
    cat_inf ~ 1 + demo_level + uni_rank_cat,
  data = imp_data_im_s1, 
  family = cumulative("probit"), 
  cores = 4
)

saveRDS(mod_inf_mi_s1, "../objects/models/mod_inf_mi_s1_220322.rds")
```

```{r}
imp_data_im_s2 <- mice::as.mids(long = imp_data_long %>% dplyr::filter(scenario == "s2"))
```

```{r}
mod_inf_mi_s2 <- brms::brm_multiple(
  formula = 
    cat_inf ~ 1 + demo_level + uni_rank_cat,
  data = imp_data_im_s2, 
  family = cumulative("probit"), 
  cores = 4
)

#saveRDS(mod_inf_mi_s2, "../objects/models/mod_inf_mi_s2_220322.rds")
```

## normality

```{r}
mod_norm_1 <- brms::brm(
   formula = cat_norm ~ 1 + demo_level + scenario + uni_rank_cat
   + (1|id)
  ,
  data = imp_data_list[[1]], 
  family = cumulative(link = "probit"),
  cores = 4
)

```

```{r}
conditional_effects(mod_norm_1, categorical = TRUE)
```
  

```{r}
mod_norm_mi <- brms::brm_multiple(
  formula = 
    cat_norm ~ demo_level + scenario + uni_rank_cat 
  + (1|id),
  data = imp_data_im, 
  family = cumulative("probit"), 
  cores = 4
)

#saveRDS(mod_norm_mi, "../objects/models/mod_norm_mi_220322.rds")
```

```{r}
summary(mod_norm_mi)
conditional_effects(mod_norm_mi, categorical = TRUE, plot = TRUE, ask = FALSE)
```

## heteroscedasticity

```{r}
mod_het_1 <- brms::brm(
  formula = 
    cat_het ~ 1 + demo_level + scenario + uni_rank_cat
   + (1|id)
  ,
  data = imp_data_list[[1]], 
  family = cumulative(link = "probit"),
  cores = 4
)
```

```{r}
summary(mod_het_1)
conditional_effects(mod_het_1, categorical = TRUE, plot = TRUE, ask = FALSE)
```

```{r}
mod_het_1_s2 <- brms::brm(
  formula = 
    cat_het ~ 1 + demo_level
  ,
  data = imp_data_list[[1]] %>% dplyr::filter(scenario == "s2"), 
  family = cumulative(link = "probit", threshold = "flexible"),
  inits = 0,
  prior = c(prior("normal(0, 4)", class = "Intercept") 
            ),
  cores = 4
)
```

```{r}
summary(mod_het_1_s2)
conditional_effects(mod_het_1_s2, categorical = TRUE, plot = TRUE, ask = FALSE)
```



```{r}
mod_het_mi <- brms::brm_multiple(
  formula = 
    cat_het ~ demo_level + scenario + uni_rank_cat 
  + (1|id),
  data = imp_data_im, 
  family = cumulative("probit"), 
  cores = 4
)

saveRDS(mod_het_mi, "../objects/models/mod_het_mi_220322.rds")
```

```{r}
summary(mod_het_mi)
conditional_effects(mod_het_mi, categorical = TRUE, plot = TRUE, ask = FALSE)
```

# data check

```{r}
data_check <- imp_data_list[[1]]
data_check %>% 
  dplyr::select(
    id, 
    world_rank, uni_rank_cat, 
    demo_level, 
    cat_norm, cat_het, cat_out, cat_inf
  ) %>% View()
```

```{r message = F}
data_check %>% 
  dplyr::group_by(cat_out, scenario) %>%
  dplyr::summarise(n = n())

data_check %>% 
  dplyr::group_by(cat_out, demo_level) %>%
  dplyr::summarise(n = n())

data_check %>% 
  dplyr::group_by(cat_out, uni_rank_cat) %>%
  dplyr::summarise(n = n())
```

```{r message = F}
data_check %>% 
  dplyr::group_by(cat_inf, scenario) %>%
  dplyr::summarise(n = n())

data_check %>% 
  dplyr::group_by(cat_inf, demo_level) %>%
  dplyr::summarise(n = n())

data_check %>% 
  dplyr::group_by(cat_inf, uni_rank_cat) %>%
  dplyr::summarise(n = n())
```


```{r message = F}
data_check %>% 
  dplyr::group_by(cat_norm, scenario) %>%
  dplyr::summarise(n = n())

data_check %>% 
  dplyr::group_by(cat_norm, demo_level) %>%
  dplyr::summarise(n = n())

data_check %>% 
  dplyr::group_by(cat_norm, uni_rank_cat) %>%
  dplyr::summarise(n = n())
```

```{r message = F}
data_check %>% 
  dplyr::group_by(cat_het, scenario) %>%
  dplyr::summarise(n = n())

data_check %>% 
  dplyr::group_by(cat_het, demo_level) %>%
  dplyr::summarise(n = n())

data_check %>% 
  dplyr::group_by(cat_het, uni_rank_cat) %>%
  dplyr::summarise(n = n())
```

## s1 -> s2 change

```{r}
s_change_dat <- imp_data_0 %>% 
  dplyr::select(id, scenario, cat_out, cat_inf, cat_norm, cat_het) %>%
  dplyr::arrange(id, scenario) %>%
  dplyr::group_by(id) %>%
  dplyr::mutate(
    out_change = cat_out[1] != cat_out[2], 
    inf_change = cat_inf[1] != cat_inf[2], 
    norm_change = cat_norm[1] != cat_norm[2], 
    het_change = cat_het[1] != cat_het[2]
  )
```


```{r}
s_change_dat %>%
  dplyr::filter(
    (any(c(out_change, inf_change, norm_change, het_change)) == TRUE) 
    | any(is.na(c(out_change, inf_change, norm_change, het_change)))
  )

s_change_dat %>%
  dplyr::select(id, scenario, cat_out, out_change) %>%
  dplyr::filter(
    out_change == TRUE
  )

s_change_dat %>%
  dplyr::select(id, scenario, cat_inf, inf_change) %>%
  dplyr::filter(
    inf_change == TRUE
  )

s_change_dat %>%
  dplyr::select(id, scenario, cat_norm, norm_change) %>%
  dplyr::filter(
    norm_change == TRUE
  )
  
s_change_dat %>%
  dplyr::select(id, scenario, cat_het, het_change) %>%
  dplyr::filter(
    het_change == TRUE
  )


```

```{r}
mod_out_diff <- brms::brm(
  formula = 
    cat_out ~ scenario 
  + (1|id),
  data = s_change_dat %>% dplyr::filter(out_change == TRUE), 
  family = "bernoulli", 
  cores = 4
)
```

```{r}
summary(mod_out_diff)
conditional_effects(mod_out_diff, plot = TRUE, ask = FALSE)
```

```{r}
re_draws_1_out_diff <- coda::as.mcmc(mod_out_diff)[[1]] %>%
  as.data.frame() %>%
  dplyr::select(contains("id")) %>%
  dplyr::mutate(
    across(.fns = exp_c)
  ) %>%
  tidyr::pivot_longer(
    cols = everything(),
    values_to = "prob", 
    names_to = "re"
  )

for(i in unique(as.character(data_1$id))){
  
  print(  
    re_draws_1_out_diff %>%
      dplyr::filter(stringr::str_detect(string = re, pattern = i)) %>%
      ggplot2::ggplot(data = ., aes(x = prob)) + 
      labs(title = i) + 
      geom_density(size = 2) + 
      theme(
        plot.title = element_text(size = 60)
      )
  )
  
}
```

